### 2014-06-30 Quality_Reports/PCR_bottleneck.Rmd
Added observation, changed orientation of x axis ticks

```{r boxplot_strand,include = TRUE,echo = FALSE,results = "hide",fig.height = 4,fig.width = 12}
tab1 = lapply(tab[3:1],function(x)rbind(data.frame(type = x$type,PBC = x$PBC_plus,strand = "+"),
  data.frame(type = x$type,PBC = x$PBC_minus,strand = "-")))
df1 = do.call(rbind,tab1)
df1$type = factor(df1$type)
df1$strand = factor(df1$strand)
p1 <- ggplot(df1,aes(strand,PBC))+geom_boxplot()+facet_grid(.~type)+
  theme(legend.position = "none",axis.text.x = element_text(angle =90))
print(p1)
```

- For this plot, the PBC coefficents was calculated using only the reads with certain strand. In particular, we can see that for all 3 types, the boxplots for both strands are very similar.

>>>>

```{r boxplot_strand,include = TRUE,echo = FALSE,results = "hide",fig.height = 4,fig.width = 12}
tab1 = lapply(tab[3:1],function(x)rbind(data.frame(type = x$type,PBC = x$PBC_plus,strand = "+"),
  data.frame(type = x$type,PBC = x$PBC_minus,strand = "-")))
df1 = do.call(rbind,tab1)
df1$type = factor(df1$type)
df1$strand = factor(df1$strand)
p1 <- ggplot(df1,aes(strand,PBC))+geom_boxplot()+facet_grid(.~type)+
  theme(legend.position = "none")
print(p1)
```

- For this plot, the PBC coefficents was calculated using only the reads with certain strand. In particular, we can see that for all 3 types, the boxplots for both strands are very similar.
- The observations of figure 1 hold for both strands.
